A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-16 sections/05-responses.tex
Change colors to grayscale.

We asked the students to evaluate their proficiency in \textit{OpenMP} and
\textit{Pthreads}, \textit{before} completing the assignment, with two sets of
questions. The first set used the same five-point scale as the other background
questions and is also shown in Figure \ref{fig:background}. The students
reported significantly larger proficiency in \textit{Pthreads} than in
\textit{OpenMP}, and the majority of the students reported they did not know
\textit{OpenMP} before the course.

@@

The percentages of \textit{Strongly Agree} (SA) and \textit{Agree} (A)
responses are significantly larger for questions $(1)$, $(3)$ and $(5)$, which
are related to \textit{OpenMP}.  Likewise, the percentages of \textit{Disagree}
(D) responses are significantly larger for questions $(2)$, $(4)$ and $(6)$,
which are related to \textit{Pthreads}. These responses lead to the conclusion
that \textbf{the perception of the students was that it was easier to use
\textit{OpenMP} than \textit{Pthreads}} to parallelize and improve the
performance of the sequential code provided in the assignment.

@@

The percentages of \textit{No Difficulty} $(1)$ and difficulty level $(2)$
responses are significantly larger for learning \textit{OpenMP}. Likewise, the
percentages of difficulty level $(4)$ and \textit{Much Difficulty} $(5)$
responses are significantly larger for learning \textit{Pthreads}.  We derive
from these responses the conclusion that \textbf{the students perceived less
difficulty to learn \textit{OpenMP} than \textit{Pthreads}} for the purposes of
the assignment.

@@

The percentage of \textit{OpenMP} selections is significantly larger for all
questions, except for questions $(7)$ and $(13)$. The responses for questions
$(7)$ -- $(12)$ strengthen the previous conclusion that the perception of the
students was that it was easier to use \textit{OpenMP} than \textit{Pthreads}
in the context of the assignment. The performance results that we obtained from
analysing the students' submissions challenge the perception of the students.
The responses to question $(13)$, extracted by our analysis, show that
\textbf{the students achieved better performance when using \textit{Pthreads}
than \textit{OpenMP}}.

>>>>

We asked the students to evaluate their proficiency in \textit{OpenMP} and
\textit{Pthreads}, \textit{before} completing the assignment, with two sets of
questions. The first set used the same five-point scale as the other background
questions and is also shown in Figure \ref{fig:background}. The students
reported larger proficiency in \textit{Pthreads} than in
\textit{OpenMP}, and the majority of the students reported they did not know
\textit{OpenMP} before the course.

@@

The percentages of \textit{Strongly Agree} (SA) and \textit{Agree} (A)
responses are larger for questions $(1)$, $(3)$ and $(5)$, which
are related to \textit{OpenMP}.  Likewise, the percentages of \textit{Disagree}
(D) responses are larger for questions $(2)$, $(4)$ and $(6)$,
which are related to \textit{Pthreads}. These responses lead to the conclusion
that \textbf{the perception of the students was that it was easier to use
\textit{OpenMP} than \textit{Pthreads}} to parallelize and improve the
performance of the sequential code provided in the assignment.

@@

The percentages of \textit{No Difficulty} $(1)$ and difficulty level $(2)$
responses are larger for learning \textit{OpenMP}. Likewise, the
percentages of difficulty level $(4)$ and \textit{Much Difficulty} $(5)$
responses are larger for learning \textit{Pthreads}.  We derive
from these responses the conclusion that \textbf{the students perceived less
difficulty to learn \textit{OpenMP} than \textit{Pthreads}} for the purposes of
the assignment.

@@

The percentage of \textit{OpenMP} selections is larger for all
questions, except for questions $(7)$ and $(13)$. The responses for questions
$(7)$ -- $(12)$ strengthen the previous conclusion that the perception of the
students was that it was easier to use \textit{OpenMP} than \textit{Pthreads}
in the context of the assignment. The performance results that we obtained from
analysing the students' submissions challenge the perception of the students.
The responses to question $(13)$, extracted by our analysis, show that
\textbf{the students achieved better performance when using \textit{Pthreads}
than \textit{OpenMP}}.
